Shapiro delay

### 2022-06-16 shapiro.Rmd
tiny changes

The Shapiro delay is one of the classical tests of general relativity.
Here I use direct numerical simulation to

@@

![Diagram of light path from Earth to Venus via grazing incidence at sun](earth_venus_sun_eddington_shapiro.png){width=100px}

>>>>

The Shapiro delay is one of the classical tests of general relativity.
In this unfinished document I use direct numerical simulation to
verify the predictions of GR.

@@

![Diagram of light path from Earth to Venus via grazing incidence at sun](earth_venus_sun_eddington_shapiro.png){width=700px}
